---
output:
  md_document:
    variant: markdown_github
---

<!-- *.md is generated from *.Rmd. Please edit that file -->

```{r}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "show/network-",
  warning = FALSE
)
```

# Network visualization with R

## igraph

from [](http://kateto.net/network-visualization)


### step1 read data

- links: describes the edges of the network. Its first two columns are the IDs of the source and the target node for each edge. The following columns are edge attributes (weight, type, label, or anything else).
- nodes: starts with a column of node IDs. Any following columns are interpreted as node attributes. This parameter can be omitted - in that case theigraph object will be generated based solely on the link structure in d.

```{r, message=F, warning=F}
library(igraph)

nodes <- read.csv("data/Dataset1-Media-Example-NODES.csv", header=T, as.is=T)
links <- read.csv("data/Dataset1-Media-Example-EDGES.csv", header=T, as.is=T)

# nodes and links data format
head(nodes, 4)
head(links, 4)

```

### igraph object

The description of an igraph object starts with four letters:

- D or U, for a directed or undirected graph
- N for a named graph (where nodes have a name attribute)
- W for a weighted graph (where edges have a weight attribute)
- B for a bipartite (two-mode) graph (where nodes have a type attribute)

The two numbers that follow (17 49) refer to the number of nodes and edges in the graph. The description also lists node & edge attributes, for example:

- (g/c) - graph-level character attribute
- (v/c) - vertex-level character attribute
- (e/n) - edge-level numeric attribute


```{r, message=F, warning=F}
# generate igraph object
net <- graph_from_data_frame(d=links, vertices=nodes, directed=F) 
net          # "net" object
E(net)       # The edges of the "net" object
V(net)       # The vertices of the "net" object

```

### plot


#### Plotting parameters

Add attributes to the igraph object.

```{r network-param, message=F, warning=F, fig.width = 6, fig.height = 5}

# basic plot
plot(net)

# remove loops in the graph
net <- simplify(net, remove.multiple = T, remove.loops = T) 
plot(net)

# Generate colors based on media type:
colrs <- c("gray50", "tomato", "gold")
V(net)$color <- colrs[V(net)$media.type]
plot(net) 

# Change node border color as node color
V(net)$frame.color <- colrs[V(net)$media.type]
plot(net) 

# Compute node degrees (#links) and use that to set node size:
deg <- degree(net, mode="all")
V(net)$size <- deg*3
plot(net) 

# We could also use the audience size value:
V(net)$size <- V(net)$audience.size*0.6
plot(net) 

# The labels are currently node IDs.
# Setting them to NA will render no labels:
V(net)$label <- NA
plot(net) 

# Set edge width based on weight:
E(net)$width <- E(net)$weight/6
plot(net) 

#change edge color:
E(net)$color <- "blue"
plot(net)

E(net)$color <- "gray80"
# We can even set the network layout:
graph_attr(net, "layout") <- layout_with_lgl
plot(net) 

# remove nodes by connectivity
f_net <- delete.vertices(net,which(degree(net)<4))
plot(f_net)

```


#### Network layouts

```{r network-layout, message=F, warning=F, fig.width = 6, fig.height = 5}
# example data
net.bg <- sample_pa(100) 
V(net.bg)$size <- 8
V(net.bg)$frame.color <- "white"
V(net.bg)$color <- "orange"
V(net.bg)$label <- "" 
E(net.bg)$arrow.mode <- 0
plot(net.bg)

# Circle layout
l <- layout_in_circle(net.bg)
plot(net.bg, layout=l)

# Fruchterman-Reingold is one of the most used force-directed layout algorithms out there.
# rather slow and therefore less often used in graphs larger than ~1000 vertices. 

l <- layout_with_fr(net.bg)
plot(net.bg, layout=l)

# Another popular force-directed algorithm that produces nice results for connected graphs is Kamada Kawai. 
l <- layout_with_kk(net.bg)
plot(net.bg, layout=l)

# The LGL algorithm is meant for large, connected graphs. 
# Here you can also specify a root: a node that will be placed in the middle of the layout.
plot(net.bg, layout=layout_with_lgl)
```

#### Highlighting aspects of the network

```{r network-highlight-asp, message=F, warning=F, fig.width = 6, fig.height = 5}
par(mfrow=c(1,2))

# Community detection (by optimizing modularity over partitions):
clp <- cluster_optimal(net)
class(clp)

# Community detection returns an object of class "communities" 
# which igraph knows how to plot: 
plot(clp, net)
 
# We can also plot the communities without relying on their built-in plot:
V(net)$community <- clp$membership
colrs <- adjustcolor( c("gray50", "tomato", "gold", "yellowgreen"), alpha=.6)
plot(net, vertex.color=colrs[V(net)$community])

```


#### Highlighting specific nodes or links

- Highlight nodes by the distance to specific nodes
```{r network-highlight-nodes, message=F, warning=F, fig.width = 6, fig.height = 5}
library(RColorBrewer)

dist.from.NYT <- distances(net, v=V(net)[media=="NY Times"], 
                           to=V(net), weights=NA)

# Set colors to plot the distances:
oranges <- colorRampPalette(c("dark red", "gold"))
col <- oranges(max(dist.from.NYT)+1)
col <- col[dist.from.NYT+1]

plot(net, vertex.color=col, vertex.label=dist.from.NYT, edge.arrow.size=.6, 
     vertex.label.color="white")

```

- Highlight path


```{r network-highlight-path, message=F, warning=F, fig.width = 6, fig.height = 5}

news.path <- shortest_paths(net, 
                            from = V(net)[media=="MSNBC"], 
                             to  = V(net)[media=="New York Post"],
                             output = "both") # both path nodes and edges

# Generate edge color variable to plot the path:
ecol <- rep("gray80", ecount(net))
ecol[unlist(news.path$epath)] <- "orange"
# Generate edge width variable to plot the path:
ew <- rep(2, ecount(net))
ew[unlist(news.path$epath)] <- 4
# Generate node color variable to plot the path:
vcol <- rep("gray40", vcount(net))
vcol[unlist(news.path$vpath)] <- "gold"

plot(net, vertex.color=vcol, edge.color=ecol, 
     edge.width=ew, edge.arrow.mode=0)

```

- Highlight the edges going into or out of a vertex

```{r network-highlight-edges, message=F, warning=F, fig.width = 6, fig.height = 5}

inc.edges <- incident(net,  V(net)[media=="Wall Street Journal"], mode="all")

# Set colors to plot the selected edges.
ecol <- rep("gray80", ecount(net))
ecol[inc.edges] <- "orange"
vcol <- rep("grey40", vcount(net))
vcol[V(net)$media=="Wall Street Journal"] <- "gold"
plot(net, vertex.color=vcol, edge.color=ecol, edge.width=2)


```

- Highlight the neighbour nodes

To find the neighbors for multiple nodes, use `adjacent_vertices()` instead of `neighbors()`. To find node neighborhoods going more than one step out, use function `ego()` with parameter `order` set to the number of steps out to go from the focal node(s).

```{r network-highlight-neighbor, message=F, warning=F, fig.width = 6, fig.height = 5}
neigh.nodes <- neighbors(net, V(net)[media=="Wall Street Journal"], mode="out")

# Set colors to plot the neighbors:
vcol[neigh.nodes] <- "#ff9d00"
plot(net, vertex.color=vcol)
```

- "mark" a group of nodes

```{r network-highlight-mark, message=F, warning=F, fig.width = 6, fig.height = 5}

par(mfrow=c(1,2))
plot(net, mark.groups=c(1,4,5,8), mark.col="#C5E5E7", mark.border=NA)

# Mark multiple groups:
plot(net, mark.groups=list(c(1,4,5,8), c(15:17)), 
          mark.col=c("#C5E5E7","#ECD89A"), mark.border=NA)

```

[[返回首页](../../README.md)]